\documentclass[11pt,a4paper,roman]{moderncv}        % possible 

\moderncvstyle{classic}                   
\moderncvcolor{green}                     
\usepackage{ragged2e} 
\usepackage[utf8]{inputenc}               
\usepackage[scale=0.8]{geometry}

% personal data
\name{Thiago Augusto Fernandes de Carvalho}
\title{}
\address{Gal. Milton Tavares de Souza, s/nº -São Domingos - Niterói - RJ - 24210-346 - Brazil}
\email{thiago_augusto@id.uff.br}
\begin{document}
\recipient{To: Huiling Chen, Feng ZHU and Quan Zou}{Editor}

\date{\today}
\opening{Dear Huiling Chen, Feng ZHU and Quan Zou,}

\closing{Yours sincerely,}
\makelettertitle

\justify

We would like to submit our manuscript entitled ``Improving the heart ejection fraction evaluation using a modified
ultrasound Vision Transformer architecture'' for publication in Computers in Biology and Medicine.

In this study, we present an enhanced approach based on the UViT network to accurately calculate the left ventricular ejection fraction (LVEF) of the heart using temporal image data. Our approach includes modifications to the UViT network's hyperparameters, such as hidden layers and batch size, to improve the network's depth and prevent overfitting. Additionally, we incorporate variations of the Bert model to further enhance the performance of our proposed architecture.

Experimental results demonstrate that the modified UViT network, in conjunction with the RoBERTa model, outperforms the standard UViT network by achieving a significant reduction in mean absolute error (MAE) from 5.88 to 4.84 and root mean square error (RMSE) from 8.38 to 6.32. This improvement indicates the enhanced approach's capability to accurately estimate the left ventricular ejection fraction (LVEF) using temporal image data.

As part of our future work, we plan to explore the application of this architecture in other medical domains that deal with temporal ultrasound image data, such as gynecology. We believe that the insights gained from this study have the potential to significantly impact the field of medical imaging and improve diagnostic capabilities.

We confirm that this manuscript has not been previously published and is not under consideration by any other journal. All co-authors have reviewed and approved the manuscript, and we declare no conflicts of interest.

We appreciate your consideration of our manuscript for publication in Computers in Biology and Medicine and look forward to receiving your valuable feedback.

Thank you for your time and attention.

Sincerely,

\makeletterclosing
\end{document}
